---
title:  "Chapter 01: Prediction as a unifying theme in statistics and causal inference"
author: "Craig Slinkman"
date: "11/14/2020"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load required directories

Note we will use the Bayesian modeling language call $stan$.  $stan$ is a probabilistic programming language for statistical inference written in C++. The Stan language is used to specify a (Bayesian) statistical model with an imperative program calculating the log probability density function. Stan is licensed under the New BSD License.  

We also use the R-package the $arm$ package.  The $arm $ contains R functions for Bayesian inference using $lm$, $glm$, $mer$ and $polr$ objects. BACCO is an R bundle for Bayesian analysis of random functions. BACCO contains three sub-packages: $emulator%, $calibrator$, and $approximator$, that perform Bayesian emulation and calibration of computer programs.
  
These two packages are loaded below.  You will need to install these packages before you run this code.

```{r}
require( tidyverse )                    # I live in the tidyverse ...   
require( readr )                        # To read table objects ...
require( rstanarm )                     # For Bayesian approach to statistics ...
require( arm )                          # Additional Bayesian functionality ...
library("bayesplot")                    # For plotting Bayesian analysis ...
theme_set(bayesplot::theme_default(base_family = "sans"))
```


## 1.2 Why learn regression

Note that I converted the hiss.dat file to a csv file.

### Reading the hibbs election data onto a tibble

```{r}
fp <- file.path( getwd(),              # Specify full path to read file ...
                 "data",
                 "hibbs.csv" )
hibbs <- read_csv( fp )                # Read the file

hibbs                                  # Verify file
```


