---
title: "Section 1.2"
author: "Andrew Gelmaan, at  all as implemnted by Craig Slinkman"
date: "12/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




Regression[1] is a method that allows researchers to summarize how predictions or average values of outcome vary across individuals defined by a set of predictors.

I live in the tidyverse and use ggplot2 to draw ggplot2 to draw my graphs.

## Loading required packages

I live in the tidyverse and use ggplot2 to draw ggplot2 to draw my graphs.

We also need to load the stand packages so we can estimate the posterior distribution using stan.

```{r}
library( tidyverse )                     # I live in the tidyverse ...
library( readr )                         # To read data in the tidyverse ...    
library( cowplot )                       # For additional graphics functionality ...
```

## Read the hibbs data

I have downloaded the data from the text website at at www.stat.columbia.edu/~gelman/regression/.
It is my practice to store the data for a project in the data subdirectory of the R-project.  I then build a file path to the file directory.  We do this below.


```{r}
cd <- getwd()                           # Get current directory ...

fp <-                                   # Construct file path to data.
  file.path( cd,
             "data",
             "hibbs.csv" )

hibbs <- read_csv( fp )                 # Read data as tibble ...

hibbs                                   # Verify hibbs tibble
```

## Draw Figure 1.1a

```{r}
figure1.1a <-   
    ggplot( hibbs,
          aes( x = growth,
               y = vote,
               label = year ) ) +
    geom_text() +
    scale_x_continuous( name   = "Average recent growth in personal income",
                        labels = scales::percent_format(accuracy = 1,
                                                        scale    = 1.0)) +
    scale_y_continuous( name   = "Incumbet party's vote share",
                        labels = scales::percent_format( accuracy = 1,
                                                         scale    = 1)) +
    ggtitle( "Forecasting incumbets vote share from the economy" ) +
    theme_cowplot()

figure1.1a
```

## Figure 1.1b


## References

[1] Gelman, Andrew; Hill, Jennifer; Vehtari, Aki. Regression and Other Stories (Analytical Methods for Social Research) (p. 4). Cambridge University Press. Kindle Edition. 